Review: Crop adaptation through introgression from wild relatives

### 2016-07-06 TiG_prospectus.tex
Li added methods part and some references

\documentclass[11pt]{article}
\usepackage{color}
\usepackage{authblk}%allows footnote format for authors
\usepackage[letterpaper, margin=1in]{geometry} %package that allows changes in margins and header/footers
\usepackage[numbers,sort]{natbib}
\bibliographystyle{ieeetr}
\newcommand{\mbh}[1]{\textcolor{orange}{ \emph{\scriptsize  #1}} } %creating command for Matt's comments
\newcommand{\lwang}[1]{\textcolor{red}{ \emph{\scriptsize  #1}} } %creating command for Li's comments
\newcommand{\gmj}[1]{\textcolor{blue}{ \emph{\scriptsize  #1}} } %creating command for Garrett's comments

@@

The recent availability of genome-wide resequencing and reduced-representation genotyping (\emph{e.g.}, GBS and RAD-Seq) data combined with new analytical methods have facilitated comprehensive study of introgression across a number of species (\textbf{Table 1}).
\begin{enumerate}
\item{High-density marker data can be used with haplotype-based and other methods to assign specific genomic regions to a taxon of origin and to identify introgression across taxa \cite{Martin2015,Price2009,Lawson2012,pease2015,rosenzweig2016,geneva2015}.}
\item{Application of these approaches across a number of plant and animal species suggests introgression can play an adaptive role. For example, introgression from ancient hominins (\emph{e.g.}, Neanderthals and Denisovans) to humans has been detected at loci controlling skin pigmentation, defense against pathogens, and toleration of high altitude (reviewed in \cite{Racimo2015}), introgression has conferred M\"{u}llerian mimicry across butterfly species (\cite{Heliconius2012}; \textbf{Figure 1}), introgression has spread insecticide resistance across mosquito species \cite{Norris2015}, and introgression across \emph{Mimulus} (\emph{i.e.}, monkeyflower) species has resulted in adaptation to pollinator preference and contributed to speciation \cite{Stankowski2015}}.
\end{enumerate}

>>>>

\documentclass[11pt]{article}
\usepackage{color}
\usepackage{authblk}%allows footnote format for authors
\usepackage[letterpaper, margin=1in]{geometry} %package that allows changes in margins and header/footers
\usepackage[numbers,sort]{natbib}
\usepackage{amsmath}
\bibliographystyle{ieeetr}
\newcommand{\mbh}[1]{\textcolor{orange}{ \emph{\scriptsize  #1}} } %creating command for Matt's comments
\newcommand{\lwang}[1]{\textcolor{red}{ \emph{\scriptsize  #1}} } %creating command for Li's comments
\newcommand{\gmj}[1]{\textcolor{blue}{ \emph{\scriptsize  #1}} } %creating command for Garrett's comments

@@

The recent availability of genome-wide resequencing and reduced-representation genotyping (\emph{e.g.}, GBS and RAD-Seq) data combined with new analytical methods have facilitated comprehensive study of introgression across a number of species (\textbf{Table 1}).
\begin{enumerate}
\item{High-density marker data can be used with haplotype-based and other methods to assign specific genomic regions to a taxon of origin and to identify introgression across taxa \cite{Martin2015,Price2009,Lawson2012,pease2015,rosenzweig2016,geneva2015}.}

The methods introduced here do not include those marginally estimating introgression/migration rate as a component in the complete demographic history, such as Approximate Bayesian Computation (ABC) \cite{beaumont2002}, diffusion approximations for demographic inference (dadi) \cite {gutenkunst2009}, sorts of isolation with migration model \cite{hey2004} and the multiple sequentially Markovian coalescent (MSMC) \cite{schiffels2014}. 
The collection of methods described different layers of genetic variation: diversity and divergence, haplotype variation and phylogenetic relationships.
We focus here on analytical prospected and limitations and introduce only a few representatives of each category.

First, genomic regions of introgression were expected to show a low level of divergence.
 F_{st} and d_{XY} as well as its derivates, such as G_{min} \cite{geneva2015} and RND_{min}\cite{rosenzweig2016}, are representatives of such statistics. 
 The former two are insensitive to rare migrants, thus limited in detecting recent introgression; while the latter two  overcame the disadvantages.

 \begin{equation}
    G_{min} = \frac{d_{min}}{d_{XY}}
 \end{equation}
 where d_{min} is the minimum sequence distance between haplotypes in species X and Y.

 \begin{equation}
 	RND_{min} = \frac{d_{min}}{d_{out}}
 \end{equation}
where d_{out} equals to $(d_{XO} + d_{YO})/2$, the average sequence distance between each species and the outgroup (O).
In addition, RND_{min} is sensitive to variable mutation rate, which reflects on the branch length to the outgroup taxa.

Second, local ancestry reconvolution (also known as chromosome painting) can identify the genomic regions that come from different source populations \cite{schraiber2015}. 
Such method usually takes phased haplotypes as input and some can even take multiple source populations, such as MULTIMIX \cite{churchhouse2013}.

Third, ABBA-BABA statistics (also known as D-statistics) and its derivatives are widely applied to search for signs of introgression in genomic patterns of shared derived variants between populations or species.

\item{Application of these approaches across a number of plant and animal species suggests introgression can play an adaptive role. For example, introgression from ancient hominins (\emph{e.g.}, Neanderthals and Denisovans) to humans has been detected at loci controlling skin pigmentation, defense against pathogens, and toleration of high altitude (reviewed in \cite{Racimo2015}), introgression has conferred M\"{u}llerian mimicry across butterfly species (\cite{Heliconius2012}; introgression has spread insecticide resistance across mosquito species \cite{Norris2015}, and introgression across \emph{Mimulus} (\emph{i.e.}, monkeyflower) species has resulted in adaptation to pollinator preference and contributed to speciation \cite{Stankowski2015}}.
\end{enumerate}
